Extracting The Power of Dependent Types

### 2021-09-22 paper.tex
Acknowledge grants.
Adding copyright.
        This will need further updates after I'll figure out the deal
        with the uninversity paying for open access.

@@

\pagebreak
%% Bibliography
\bibliography{paper}

>>>>

%%% FIXME I am didnt update publishing rights yet, as I am waiting for
%%% the university to comeback with the payment instructions for open access.

%%% If you see 'ACMUNKNOWN' in the 'setcopyright' statement below,
%%% please first submit your publishing-rights agreement with ACM (follow link on submission page).
%%% Then please update our instructions page and copy-and-paste the NEW commands into your article.
%%% Please contact us in case of questions; allow up to 10 min for the system to propagate the information.
%%%
%%% The following is specific to GPCE '21 and the paper
%%% 'Extracting the Power of Dependent Types'
%%% by Artjoms Šinkarovs and Jesper Cockx.
%%%
\setcopyright{rightsretained} % XXX ENSURE THAT THIS VALUE IS CORRECT!!!
\acmPrice{15.00}
\acmDOI{10.1145/3486609.3487201}
\acmYear{2021}
\copyrightyear{2021}
\acmSubmissionID{splashws21gpcemain-p18-p}
\acmISBN{978-1-4503-9112-2/21/10}
\acmConference[GPCE '21]{Proceedings of the 20th ACM SIGPLAN International Conference on Generative Programming: Concepts and Experiences}{October 17--18, 2021}{Chicago, IL, USA}
\acmBooktitle{Proceedings of the 20th ACM SIGPLAN International Conference on Generative Programming: Concepts and Experiences (GPCE '21), October 17--18, 2021, Chicago, IL, USA}

@@

\begin{acks}
We would like to thank reviewers for their constructive suggestions.
This work is supported by the \grantsponsor{EPSRC}{Engineering and Physical
Sciences Research Council}{https://epsrc.ukri.org} through the grant
\grantnum{EPSRC001}{EP/N028201/1}.
\end{acks}

%\pagebreak
%% Bibliography
\bibliography{paper}
